\textit{MSF: Modulated Sub-graph Finder}

### 2018-05-22 MSF_Paper_FA.tex
Add files via upload

\usepackage{subcaption}
\usepackage{hyperref}
\newcommand{\FA}[1]{\begingroup\color{magenta}#1\endgroup}
\newcommand{\TODO}[1]{\begingroup\color{red}#1\endgroup}
%opening
\begin{document}

@@

Source code:
https://github.com/MariamFarman/Modulated-SubGraph-Finder \newline Software
license: Creative Commons Attribution 4.0 International License

@@

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{10 cm}
	\includegraphics[width=1.0\linewidth]{MSFvsReactomeUpsetPlot}
	\caption{The Upset plot shows the number of common pathways between different time-point and cut offs. }
	\label{fig:msfvsreactome}
\end{minipage}
}
\end{figure*}

>>>>

\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{pdfpages}
\newcommand{\FA}[1]{\begingroup\color{magenta}#1\endgroup}
\newcommand{\TODO}[1]{\begingroup\color{red}#1\endgroup}
%opening
\begin{document}

@@

\noindent
Source code:
https://github.com/MariamFarman/Modulated-SubGraph-Finder \newline Software
license: Creative Commons Attribution 4.0 International License

@@

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{10 cm}
	\includegraphics[width=1.0\linewidth]{MSFvsReactomeUpsetPlot}
	\caption{The Upset plot shows the number of shared pathways between different time-point and cut offs. All the different toll-like receptor signaling pathways identified from \texttt{MSF} identified genes are marked. }
	\label{fig:msfvsreactome}
\end{minipage}
}
\end{figure*}
